R for Clinical Study Reports and Submission

### 2021-10-13 submission-package.Rmd

The demo project (R package) we will prepare for submission is called [`esubdemo`](https://github.com/elong0527/esubdemo.git) available on GitHub.
You can download or clone it:

@@

To prepare R packages for submission, one needs to pack the packages into a text files, and then verify if the file only contains ASSCII.
With packed packages, one can unpack and install them from the text file, too.

>>>>

The demo project (R package) we will prepare for submission is called [`esubdemo`](https://github.com/elong0527/esubdemo) available on GitHub.
You can download or clone it:

@@

To prepare R packages for submission, one needs to pack the packages into text files, and then verify if the file only contains ASSCII characters.
With packed packages, one can unpack and install them from the text file, too.
